% LaTeX source of my resume (FR/EN)
% =================================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.

% Start a document with the here given default font size and paper size.
\documentclass[10pt,letterpaper]{article}

\usepackage{etoolbox}
\newtoggle{french}
\newtoggle{1colsummary}
\newtoggle{2colsummary}


% Use 1colsummary by default, comment to unused
\toggletrue{1colsummary}
%\toggletrue{2colsummary}

% =============================================
% If French is disabled, use English by default
% Comment the line below to use English
% ---------------------------------------------
\toggletrue{french}
% =============================================

% Set the page margins.
\usepackage[letterpaper,margin=0.5in]{geometry}

% Setup the language.
\iftoggle{french}
{\usepackage[french]{babel}}
{\usepackage[english]{babel}}

\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}

% Allows us to use \shortdate
\usepackage[nodayofweek]{datetime}

\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins

% title on top of the document
\maintitle{Ferdian Pratama}{%
  \iftoggle{french}
   {Conseiller Principal - IA et apprentissage automatique}
   {Senior Consultant - AI \& Machine Learning}
}{%
  \iftoggle{french}
  {Dernière mise à jour le}
  {Last update on} \shortdate\today
}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:fp9821@gmail.com}{fp9821@gmail.com}\sbull
\textsmaller{+}1 
(873) 662-2529\sbull
%\href{http://www.github.com/noxouille}{github.com/noxouille}\sbull
\href{http://linkedin.com/in/ferdipratama}{linkedin.com/in/ferdipratama}
\\
989 rue de Honfleur\sbull
Sherbrooke, J1N1C9\sbull
Québec\sbull
Canada

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

% ----- 1 col summary BEGIN
\iftoggle{1colsummary}{%
\roottitle{%
  \iftoggle{french}
  {Sommaire}
  {Summary}
}

\iftoggle{french}{%
Professionnel orienté vers la qualité du produit final avec 8 ans d'expérience et une connaissance confirmée de la recherche et développement en IA, de l'analyse de données, et de la planification de projets. Je suis fier d’écrire un code propre, concis, facile à lire et à mettre à jour. 
% Présentement, je perfectionne mon experience dans le domaine de l'infrastructure d'infonuagique et de l'automatisation de l'architecture afin d'y poursuivre ma carrière.
Présentement, je suis à la recherche de nouveaux défis.
}{%
Quality-oriented professional with 8 years of experience and a proven knowledge of AI research and development, data analysis, and project planning. I take pride in writing clean, concise, maintainable, and easy-to-read code. 
% Currently honing my experience and pursuing my career in Cloud Architecture and Infrastructure Automation. 
Currently looking for new challenges.
}

\spacedhrule{0.5em}{-0.4em}
}
% ----- 1 col summary END

% ----- 2 col summary BEGIN
\iftoggle{2colsummary}{%
\roottitle{%
  \iftoggle{french}
  {Sommaire}
  {Summary}
}

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{%
  \iftoggle{french}{%
  Professionnel orienté vers la qualité du produit final avec 5 ans d'expérience et une connaissance confirmée de l'analyse de données, de la recherche et développement et de la planification de projets. Je suis fier d’écrire un code propre, concis, facile à lire et à mettre à jour. Présentement, je perfectionne mon experience dans le domaine de l'intelligence d'affaire afin d'y poursuivre ma carrière.
  }{%
  Quality-oriented professional with 5 years of experience and a proven knowledge of data analysis, research and development, and project planning. I take pride in writing clean, concise, maintainable, and easy-to-read code. Currently honing my experience and pursuing my career in Business Intelligence field.
  }
}
\\
\\
At the age of seven (1989) Cies wrote his first lines of code in a \acr{LOGO}-like language on an \acr{MSX} (pre-\acr{PC}).  Two years later he attended a conference on an emerging new technology, the Internet, at the Erasmus University from which he would graduate 16 years later (2000) with a degree in Business Computer Science.

After being introduced to the open source movement in 1997, he taught himself a variety of skills including system administration and programming (Bash, Python, Ruby \& \CPP).  By 2002 he got his pet project \acr{KT}urtle ---a zero-entry-barrier programming environment--- included in \acr{KDE}'s \emph{edu} module, and thereby in almost every Linux distribution.

Extensively travelled Europe and Asia after graduating. On return his professional life became a mix of hands-on work in startups and web software agencies, while settling as a husband and father in personal life.
\end{multicols}


\spacedhrule{0em}{-0.4em}
}
% ----- 2 col summary END

\roottitle{%
  \iftoggle{french}
  {Expériences Professionnelles}
  {Experience}
}

\headedsection
  {\href{https://www.cgi.com/en}{\acr{CGI}}}
  {\textsc{Sherbrooke, \acr{QC}}} {%
  
    % \headedsubsection{
    % \iftoggle{french}
    %   {Future position (FR) at \acr{CGI}}
    %   {Future position at \acr{CGI}}
    % }{
    % \iftoggle{french}
    %   {Depuis sept.\ '20}
    %   {Since Sept.\ '20}
    % }
    % {\bodytext{%
    %   \iftoggle{french}{%
    %     \acr{CGI} is a Canadian global information technology (\acr{IT}) consulting, systems integration, outsourcing, and solutions company. My responsibility covers mainly \acr{ETL} using Talend.
    %     }{
    %     \acr{CGI} is a Canadian global information technology (\acr{IT}) consulting, systems integration, outsourcing, and solutions company. My responsibility covers mainly \acr{ETL} using Talend.
    % }}}
    

    \headedsubsection{%
      \iftoggle{french}
      {Conseiller Principal - IA et apprentissage automatique}
      {Senior Consultant - AI \& Machine Learning}
    }{%
      \iftoggle{french}
      {Depuis sept.\ '20}
      {Since Sept.\ '20}
    }{%
    \bodytext{%
      \iftoggle{french}{%
    %   \acr{CGI} est une entreprise Canadienne d’envergure mondiale de services-conseils en technologie de l’information, d’intégration de systèmes, d'impartition et de solutions. 
%      Ma responsabilité couvre principalement le traitement d’\acr{ETL} avec Talend.
	  \renewcommand{\labelitemi}{$\bullet$}
	  \begin{itemize}
      \item Configurer et tester les outils, les composantes logicielles, les environnements de développement et de déploiement en continu (DevOps).
      \item Supporter l'opérationallisation et le déploiement des solutions de données.
      \item Proposer des solutions techniques en collaboration avec les concepteurs.
      \item Assurer le support à l'exploitation des solutions techniques mises en place: surveillance des plateformes et outils, disponibilité des plateformes, surveillance des solutions analytiques déployées.
      \end{itemize}
      }{%
    %   \acr{CGI} is a Canadian global information technology (\acr{IT}) consulting, systems integration, outsourcing, and solutions company. 
%      My responsibility covers mainly \acr{ETL} using Talend.
      \begin{itemize}
      \item Develop architecture and infrastructure solutions via Azure DevOps and Terraform.
      \item Manage administration and DevOps of DataSolutions platforms for other lines of business.
      \item Enforce best practice of data engineering and data science for Databricks and AzureML.
      \item Propose technical solutions in collaboration with Data Designers.
      \end{itemize}
  }}}

  \headedsubsection{%
    \iftoggle{french}
    {D\'eveloppeur \acr{BI}}
    {\acr{BI} Developer}
  }{%
    \iftoggle{french}
    {octobre '19 -- avril '20}
    {Oct.\ '19 -- Apr.\ '20}
  }{%
    \bodytext{%
      \iftoggle{french}{%
    %   \acr{CGI} est une entreprise Canadienne d’envergure mondiale de services-conseils en technologie de l’information, d’intégration de systèmes, d'impartition et de solutions. 
%      Ma responsabilité couvre principalement le traitement d’\acr{ETL} avec Talend.
	  \renewcommand{\labelitemi}{$\bullet$}
	  \begin{itemize}
      \item Concevoir, développer et déployer des solutions de BI, en mettant l’accent sur ETL et la migration des données avec Talend pour l’entreprise BRP.
      \item Réaliser les test unitaires, le débogage, la surveillance et le dépannage des solutions de BI.
      \item Evaluer et améliorer les solutions de BI existantes.
      \end{itemize}
      }{%
    %   \acr{CGI} is a Canadian global information technology (\acr{IT}) consulting, systems integration, outsourcing, and solutions company. 
%      My responsibility covers mainly \acr{ETL} using Talend.
      \begin{itemize}
      \item Design, build and deploy BI solutions, with emphasis on ETL and data migration using Talend for BRP Sherbrooke.
      \item Conduct unit testing, debugging, monitoring and troubleshooting BI solutions.
      \item Evaluate and improve existing BI solutions.
      \end{itemize}
  }}}

}

\headedsection
  {\href{https://www.ask-corp.jp}{\acr{ASK} Corporation}}
  {\textsc{Tokyo, \acr{JP}}} {%
  \headedsubsection{%
    \iftoggle{french}
    {Scientifiques de Données}
    {Data Scientist}
  }{%
    \iftoggle{french}
    {avril '18 -- juin '19}
    {Apr.\ '18 -- June '19}
  }{%
    \bodytext{%
      \iftoggle{french}{%
      \acr{ASK} Corporation est l'un des principaux distributeurs de composants \acr{PC} au Japon.
      \renewcommand{\labelitemi}{$\bullet$}
      \begin{itemize}
      	\item Fournir des services de conseil et concevoir des solutions Deep Learning basées sur les exigences des clients.
      	\item Augmentation des ventes de matériels Deep Learning basés sur le conseil et la gestion de contenu, générant un taux de profit de 35\%.
      \end{itemize}
      }{%
      \acr{ASK} Corporation is one of the leading distributors of \acr{PC} parts in Japan.
      \begin{itemize}
      \item Provide consulting service and devise Proof of Concept deep learning solutions based on clients' requirements.
      \item Increased the sales of deep learning hardwares based on consulting and \acr{PoC} resulting in 35\% profit rate.
      \end{itemize}
}}}}

\headedsection 
  {\href{https://mjirobotics.co.jp/en/}{\acr{MJI} Robotics}}
  {\textsc{Tokyo, \acr{JP}}} {%
  \headedsubsection{%
    \iftoggle{french}
    {Ingénieur R\&D Principal, Administrateur de Serveur}
    {Lead \acr{R\&D} Engineer, Server Administrator}
  }{%
    \iftoggle{french}
    {mars '17 -- mars '18}
    {Mar.\ '17 -- Mar.\ '18}
  }{%
    \bodytext{%
      \iftoggle{french}{%
      \acr{MJI} Robotics développe un robot assistant appelé ``\acr{TAPIA}''.
      \renewcommand{\labelitemi}{$\bullet$}
      \begin{itemize}
      	\item Réussite du projet ``Nurse \acr{TAPIA}'' pour les maisons de retraite utilisant Deep Learning pour surveiller le statut du patient dans chaque chambre.
      	\item Modèles formés et déployés pour la détection d'objets et l'image captioning avec TensorFlow et TensorRT.
      	\item Maintenance de l'infrastructure du serveur de production d'\acr{IA}, assurant un débit élevé et une latence faible.
      \end{itemize}
      }{%
      \acr{MJI} Robotics develops \acr{TAPIA}, a communication robot.
      \begin{itemize}
      \item Delivered Nurse \acr{TAPIA} project for nursing home using deep learning to monitor patient status in each room.
      \item Trained and deployed models for object detection and image captioning with TensorFlow and TensorRT.
      \item Maintained the \acr{AI} production server infrastructure, ensuring high throughput and low latency.
      \end{itemize}
}}}}

\headedsection
  {\href{http://www.plenrobotics.com/en/index.html}{Plen Robotics}}
  {\textsc{Osaka, \acr{JP}}} {%
%{\href{http://edu.kde.org/kturtle}{edu.kde.org/kturtle}} {
  \headedsubsection{%
    \iftoggle{french}
    {Stagiaire en Génie Logiciel}
    {Software Engineer Intern}
  }{
    \iftoggle{french}
    {sept.\ '16 -- déc.\ '16}
    {Sept.\ '16 -- Dec.\ '16}
  }{%
    \bodytext{
      \iftoggle{french}{%
    %   Plen Robotics développe des séries de robots miniatures pour le divertissement.
    %   \renewcommand{\labelitemi}{$\bullet$}
    %   \begin{itemize}
    %   	\item Développement de la fonctionnalité d'affichage d'art d'album Plen\acr{CUBE} à l'aide de \acr{ROS} en C ++ et de son prototype d'application Android.
    %   	\item Implémentation du protocole de partage de fichiers pour synchroniser, afficher et partager vos photos de Plen\acr{CUBE} sur votre smartphone.
    %   	\item Réduction de la latence de diffusion vidéo de 73\% en 3 jours.
    %   \end{itemize}
      }{%
    %   Plen Robotics develops miniature robot series for entertainment.
    %   \begin{itemize}
    %   \item Developed Plen\acr{CUBE} album art display feature using \acr{ROS} in C++ and its Android App prototype.
    %   \item Implemented file sharing protocol to sync, view and share your photos from Plen\acr{CUBE} to your smartphone.
    %   \item Reduced video streaming latency by 73\% within 3 days.
    %   \end{itemize}
}}}}

\vspace{-0.2em}
\begin{center}
\iftoggle{french}{%
\textit{Veuillez vous référer à \href{http://linkedin.com/in/ferdipratama}{mon profil LinkedIn} pour la liste complète de mes expériences professionnelles avec des recommandations.}
}{%
\textit{Please refer to \href{http://linkedin.com/in/ferdipratama}{my LinkedIn profile} for the complete list of work experiences along with recommendations.}
}
\end{center}


\spacedhrule{-0.2em}{-0.4em}

\roottitle{
  \iftoggle{french}
  {Parcours Scolaire}
  {Education}
}

\headedsection
  {\href{https://www.jaist.ac.jp/english/}{\acr{JAIST}}}
  {\textsc{Ishikawa, 
    \iftoggle{french}
    {Japon}
    {Japan}
  }} {

  \headedsubsection{%
    \iftoggle{french}{%
    Doctorat en philosophie \textnormal{(Science de l'information)}
    }{%
    Doctor of Philosophy \textnormal{(Information Science)}
  }}
  {2013 -- 2016} {}
%{\bodytext{Focussed on the economics of open source, rapid application development (\acr{RAD}) and the semantic web technology stack (\acr{RDF}/\acr{RDFS}, \acr{OWL} and \acr{SPARQL}).}}
%}

  \headedsubsection{%
    \iftoggle{french}{%
    Maîtrise ès sciences \textnormal{(Science de l'information)}
    }{%
    Master of Science \textnormal{(Information Science)}
  }}
  {2011 -- 2013} {}
}

\headedsection
  {\href{https://www.sgu.ac.id/}{Swiss German University}}
  {\textsc{\acr{BSD} City, 
    \iftoggle{french}
    {Indonesie}
    {Indonesia}
  }} {

  \headedsubsection{%
    \iftoggle{french}{%
    Baccalauréat en génie \textnormal{(Mécatronique)}
    }{%
    Bachelor of Engineering \textnormal{(Mechatronics)}
  }}
  {2006 -- 2010} {}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{
  \iftoggle{french}
  {Compétences Clés}
  {Skills}
}

\inlineheadsection{%
  Certification:
  }{%
    Databricks Solutions Architect Champion, Azure Data Scientists, Azure Fundamentals, DeltaLake
}

\vspace{
\iftoggle{french}
{1em}
{0em}
}

\inlineheadsection{% Special section that has an inline header with a 'hanging' paragraph
  \iftoggle{french}
  {Stack:}
  {Stack:}
  }
  {Databricks, AzureML, Azure OpenAI, Azure DevOps, Terraform, Snowflake, Ansible, Docker, Git
  }

\vspace{
\iftoggle{french}
{1em}
{0em}
}

\inlineheadsection{%
  \iftoggle{french}
  {Langages de Programmation:}
  {Programming Languages:}
  }
  {Python, bash, Powershell, C++, Scala
  }

\vspace{
\iftoggle{french}
{1em}
{0em}
}

\inlineheadsection{%
  \iftoggle{french}
  {Langues:}
  {Languages:}
  }{%
%    \iftoggle{french}{%
%    Indonésien \textit{(natif)}, Anglais \textit{(courant)}, Japonais \textit{(\acr{JLPT} N3)} et Français \textit{(A2)}.
%    }{%
%    Indonesian \textit{(native)}, English \textit{(fluent)}, Japanese \textit{(\acr{JLPT} N3)}, and French \textit{(A2)}.
    \iftoggle{french}{%
    Français \textit{(avancé)}, Anglais \textit{(bilingue)}, Japonais \textit{(avancé)} et Indonésien \textit{(langue maternelle)}.
    }{%
    English \textit{(fluent)}, French \textit{(advanced)}, Japanese \textit{(advanced)} and Indonesian \textit{(native)}.
}}

%\spacedhrule{1.6em}{-0.4em}
%
%\roottitle{Interests}
%
%\inlineheadsection
%  {Non-exhaustive and in alphabetical order:}
%  {art, Buddhism, cryptography, functional programming, Go (board game), history, music (from classical and jazz to Berlin-techno), \acr{NLP}, permaculture, philosophy, rock climbing, startups, travel, typography (e.g.\ graphic design, \LaTeX), \acr{UX}-design and vegan cuisine.}


\end{document}

